How and Why to run a Hack Week

### 2017-08-29 sections/why.tex

\item{\textit{Interdisciplinary research}: Intensive, time-bounded collaborative events are an excellent opportunity to experiment with concepts, questions, and methods that span boundaries within and across disciplines. Despite the fact that such interdisciplinary experiments are highly impactful \cite{Hall2012-hi}, they are often discouraged in risk averse traditional academia \footnote{\url{https://www.ncbi.nlm.nih.gov/labs/articles/12970550} and \url{https://www.researchgate.net/publication/8126355_EDUCATION_Risks_and_Rewards_of_an_Interdisciplinary_Research_Path}}.

@@

\item{\textit{It's fun}: Hack weeks provide a respite from day-to-day research activities and provide a low-stress venue to learn new skills and attempt high-risk projects.}
\end{itemize}

>>>>

\item{\textit{Interdisciplinary research}: Intensive, time-bounded collaborative events are an excellent opportunity to experiment with concepts, questions, and methods that span boundaries within and across disciplines. Despite the fact that such interdisciplinary experiments are highly impactful \cite{Hall2012-hi}, they are often discouraged in risk averse traditional academia \footnote{\url{https://www.ncbi.nlm.nih.gov/labs/articles/12970550} and \url{https://www.researchgate.net/publication/8126355_EDUCATION_Risks_and_Rewards_of_an_Interdisciplinary_Research_Path}}}.

@@

\item{\textit{It's fun}: Hack weeks provide a respite from day-to-day research activities and provide a low-stress venue to learn new skills and attempt high-risk projects.}

\end{itemize}
